---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  message = FALSE,
  #out.width = "100%"
  fig.width = 5,
  fig.height = 5
)
```

# rgamer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/yukiyanai/rgamer.svg?branch=master)](https://travis-ci.org/yukiyanai/rgamer)
[![Codecov test coverage](https://codecov.io/gh/yukiyanai/rgamer/branch/master/graph/badge.svg)](https://codecov.io/gh/yukiyanai/rgamer?branch=master)
<!-- badges: end -->

## Overview

The goal of `rgamer` is to help students learn Game Theory using R.
The functions provided by the package not only solve basic games such as two-person normal-form games but also provides the users with visual displays that highlight some aspects of the games --- game matrices, best response correspondence, etc.
In addition, it suggests some numerical solutions for games of which it is difficult --- or even seems impossible --- to derive a closed-form analytic solution.


## Installation

<!--
#You can install the released version of rgamer from [CRAN](https://CRAN.R-project.org) with:
``` {r}
install.packages("rgamer")
```
-->

You can install the development version from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("yukiyanai/rgamer")
```

## Example

```{r}
library(rgamer)
```

### Example 1

An example of a normal-form game:

- Player: \{Kicker, GK \}
- Strategy: \{(left, right), (left, right)\}
- Payoff: \{(-1, 1, 1, -1), (1, -1, -1, 1)\}

First, you define the game by `normal_form()`:
```{r}
game1 <- normal_form(
  players = c("Kicker", "GK"),
  s1 = c("left", "right"), 
  s2 = c("left", "right"),
  p1 = c(-1, 1, 1, -1), 
  p2 = c(1, -1, -1, 1))
```

Then, you can pass it to `solve_nfg()` function to get the table of the game (not shown here) and the Nash equilibrium.
```{r}
s_game1 <- solve_nfg(game1, mixed = TRUE, show_table = FALSE)
```

For a 2-by-2 game, you can plot the best response correspondences as well.
```{r}
s_game1$br_plot
```



### Example 2

An example of a normal-form game:

- Player: \{ A, B \}
- Strategy: \{$x \in [0, 30]$, $y \in [0, 30]$ \}
- Payoff: \{$f_x(x, y) = -x^2 + (28 - y)x$, $f_y(x, y) = -y^2 + (28 - x) y$\}

You can define a game by specifying payoff functions as character vectors using `normal_form()`:
```{r}
game2 <- normal_form(
  players = c("A", "B"),
  p1 = "-x^2 + (28 - y) * x",
  p2 = "-y^2 + (28 - x) * y",
  par1_lim = c(0, 30),
  par2_lim = c(0, 30),
  pars = c("x", "y"))
```

Then, you can pass it to `solve_nfg()`, which displays the best response correspondences by default.
```{r}
s_game2 <- solve_nfg(game2)
```


### Example 3

An example of a normal-form game:

- Player: \{ A, B \}
- Strategy: \{$x \in [0, 30]$, $y \in [0, 30]$ \}
- Payoff: \{$f_x(x, y) = -x^a + (b - y)x$, $f_y(x, y) = -y^s + (t - x) y$\}

You can define a normal-form game by specifying payoffs by R functions.
```{r}
f_x <- function(x, y, a, b) {
  -x^a + (b - y) * x
}
f_y <- function(x, y, s, t) {
  -y^s + (t - x) * y
}
game3 <- normal_form(
  players = c("A", "B"),
  p1 = f_x,
  p2 = f_y,
  par1_lim = c(0, 30),
  par2_lim = c(0, 30),
  pars = c("x", "y"))
```

Then, you can approximate a solution numerically by `solve_nfg()`. Note that you need to set the parameter values of the function that should be treated as constants by arguments `cons1` and `cons2`, each of which accepts a named list. In addition, you can suppress the plot of best responses by `plot = FALSE`.
```{r}
s_game3 <- solve_nfg(
  game = game3,
  cons1 = list(a = 2, b = 28),
  cons2 = list(s = 2, t = 28),
  plot = FALSE
)
```

You can increase the precision of approximation by `precision` (default is `1`), which takes a natural number.
```{r}
s_game3b <- solve_nfg(
  game = game3,
  cons1 = list(a = 2, b = 28),
  cons2 = list(s = 2, t = 28),
  precision = 3
)
```

